### 2022-10-14 AISTATS2023/paper.tex
latest

\begin{abstract}
Accumulated Local Effects (ALE) is a popular explainable AI method that quantifies how a feature influences the decisions of a model, handling well feature correlations. In case of complex interactions between features, instance-level feature effects may deviate from the ALE curve. It is therefore crucial to quantify this deviation, namely, the uncertainty of the effect. In this work, we define Uncertainty-aware ALE (UALE) to quantify and visualize, on a single plot, both the average effect and its uncertainty. We show that UALE quantifies uncertainty effectively, even in case of correlated features. We also note that as in ALE, UALE's approximation requires partitioning the feature domain into non-overlapping intervals (bin-splitting). The average effect and the uncertainty are computed from the instances that lie in each bin. We formally prove that to achieve an unbiased approximation of the uncertainty in each bin, bin-splitting must follow specific constraints. Based on this, we propose a method to determine the optimal intervals, \todo{balancing the estimation bias and variance.} We demonstrate, through synthetic and real datasets, (a) the advantages of modeling the uncertainty with UALE compared to alternative methods and (b) the effectiveness of UALE's appropriate bin splitting for a \todo{good} approximating of the average effect and its uncertainty.
\end{abstract}

@@

Recently, Machine Learning (ML) has been widely adopted in mission critical domains,
such as healthcare and finance. In such high-stakes areas,  it is important not only to provide accurate predictions but also meaningful explanations. For this reason, there is an increased interest in Explainable
AI (XAI). XAI literature distinguishes between local and global
methods~\citep{Molnar2020interpretable}. Local methods provide
instance-level explanations, i.e., explain the prediction for a
specific instance, whereas global methods summarize the entire model
behavior. Global methods create a global explanation by aggregating the
instance-level explanations into a single interpretable outcome,
usually a number or a plot.

A popular class of global XAI are feature effect (FE)
methods~\citep{Gromping2020MAEP} that quantify the average (over all
instances) effect of a single feature on the output\footnote{FE
  methods also isolate the combined effect of a pair of features to
  the output. Combinations of more than two features are uncommon,
  since they are difficult to estimate and visualize.}. There are
three widely-used FE methods: \emph{Partial Dependence Plots}
(PDP)\citep{friedman2001greedy}, \emph{Marginal Plots}
(MP)\citep{apley2020visualizing} and \emph{Accumulated Local Effects}
(ALE)\citep{apley2020visualizing}. ALE is established as the
state-of-the-art in quantifying the average effect, since PDP and MP
have been criticized~\citep{Gromping2020MAEP} of providing misleading explanations in case of  correlated input features.

When complex interactions between features exist, the instance-level
(local) feature effects may exhibit significant deviation, aka heterogeneity, from the aggregated (global)
explanation, a phenomenon known as aggregation
  bias~\citep{mehrabi2021survey}. We call this deviation \emph{the uncertainty of the global effect}. Aggregation bias leads to
ambiguities; for example, a feature with zero average effect may
indicate (a) no effect on the output or (b) an effect that is highly
positive for some instances and highly negative for some others. As a
result, there is a need for FE methods to quantify the deviation (uncertainty) of
instance-level explanations, in addition to the average effect. In the
case of PDP, such deviation is visualized via the Individual
Conditional Explanations (ICE)~\citep{goldstein2015peeking}. ICE
plots, however, have the same limitations as PDP in case of correlated
features. No method to quantify the deviation of instance-level effects has been proposed for ALE.

In this work, we propose UALE, a global feature-effect method that
extends ALE for modeling the uncertainty of the feature effect.
Our method handles well cases with correlated features. 
As in ALE, we provide an interval-based formulation of UALE. 
This formulation partitions the feature domain into non-overlapping 
intervals (bin-splitting) and defines the average effect (bin-effect) and its uncertainty (bin-uncertainty). We exploit this formulation to provide an UALE approximation. 
As we formally prove, a fixed equi-width partitioning that does not consider
the characteristics of the instance-level effects, which is the case in ALE, 
may lead to an erroneous (biased) estimation of the uncertainty. 
Therefore, we propose a variable-width partitioning that leads to an unbiased approximation.

The contributions of this
paper are:
\begin{itemize}
\item A global feature effect method (UALE) that quantifies both the
  average effect and its uncertainty, i.e.,~the deviation of
  instance-level effects.
\item An unbiased approximation of the uncertainty through a dynamic
  variable-size bin partitioning of the feature domain.
\item The evaluation of UALE on both synthetic and real datasets.
\end{itemize}

@@

In the rest of the paper, we use following notation. Let \(\mathcal{X} \in \mathbb{R}^d\) be the \(d\)-dimensional feature
space, \(\mathcal{Y} \in \mathbb{R}\) the target space and
\(f(\cdot) : \mathcal{X} \rightarrow \mathcal{Y}\) the black-box
function. We use index \(s \in \{1, \ldots, d\}\) for the feature of
interest and \(c = \{1, \ldots, d\} - s\) for the set with all other
indexes. For convenience, we denote the feature vector
\(\xb = (x_1, \cdots , x_s, \cdots, x_D)\) with \((x_s, \xc)\) and the
corresponding random variables
\(X = (X_1, \cdots , X_s, \cdots, X_D)\) with \((X_s, X_c)\). The
training set is \(\mathcal{D} = \{(\xb^i, y^i)\}_{i=1}^N\) sampled
i.i.d. from the distribution \(\mathbb{P}_{X,Y}\). Finally, we use
\(f^{\mathtt{<method>}}(x_s)\) for denoting the \(s\)-th FE, where
\(\mathtt{<method>}\) indicates the particular method in use, for
example ALE. An extensive list with all symbols used in this paper is
provided at Appendix~\ref{sec:list-with-symbols}.

\subsection{Feature Effect Methods}
\label{sec:feat-effect-meth}
The three well-known feature effect methods are: \emph{Partial
  Dependence Plots} (PDP), \emph{Marginal Plots} (MP) and
\emph{Accumulated Local Effects} (ALE).  PDP formulates the global FE
as an expectation over the distribution of \(X_c\), i.e.,
\(f^{\mathtt{PDP}}(x_s) = \mathbb{E}_{X_c}[f(x_s,X_c)]\), whereas MP
as an expectation over the distribution of \(X_c|X_s\), i.e.,
\(f^{\mathtt{MP}}(x_s) = \mathbb{E}_{X_c|x_s}[f(x_s, X_c)]\). Both
methods suffer from misestimations in case of correlated features. PDP
integrates over unrealistic instances and MP computes aggregated
effects, i.e., imputes the combined effect of sets of features to a
single feature~\citep{apley2020visualizing}.

@@

ICE plots and similar methods (e.g., d-ICE
plots~\citep{goldstein2015peeking}) provide a set of curves
illustrated on top-of PDP. Each curve corresponds to one instance of
the dataset, \(f^{\mathtt{ICE}}_i(x_s) = f(x_s, \xc^i)\). The user
then visually observes if the curves are homogeneous, i.e., all
instances have similar effect plots, and to what extent they deviate
from the PDP. There are methods try to automate the aforementioned
visual exploration, by grouping ICE plots into
clusters~\citep{molnar2020model, herbinger2022repid,
  britton2019vine}. Unfortunately, these methods are subject to the
failure modes of PDPs in cases of correlated
features~\citep{baniecki2021fooling}, as we also confirm in our
experimental analysis (c.f., Section~\ref{sec:simulation-examples-1}).

@@

To the best of our knowledge, no work exist so far that quantifies the
heterogeneous effects (uncertainty) based on the formulation of ALE.

@@

ALE is estimated from the available dataset instances. \citep{apley2020visualizing} proposed to divide the feature
domain in \(K\) bins of equal size and to estimate the local effects
in each bin by evaluating the model \(f\) at the bin limits:

\begin{equation}
  \label{eq:ALE_accumulated_mean_est}
  \hat{f}^{\mathtt{ALE}}(x_s) = \sum_{k=1}^{k_x} \frac{1}{|\mathcal{S}_k|} \sum_{i:\mathbf{x}^i \in
    \mathcal{S}_k} \left [ f(z_{k}, \xc^i) - f(z_{k-1}, \xc^i)) \right ]
\end{equation}
%
where \(k_x\) the index of the bin that \(x_s\) belongs to,
i.e. \(k_x: z_{k_x-1} \leq x_s < z_{k_x} \) and \(\mathcal{S}_k\) is
the set of training instances of the \(k\)-th bin, i.e.
\( \mathcal{S}_k = \{ \xb^i : z_{k-1} \leq x^i_s < z_{k} \}
\). \citep{gkolemis22} proposed the Differential ALE (DALE) that
computes the local effects on the training instances using
auto-differentiation:
\begin{equation}  \label{eq:DALE_accumulated_mean_est}
  \hat{f}^{\mathtt{DALE}}(x_s) = \Delta x \sum_{k=1}^{k_x} \frac{1}{|\mathcal{S}_k|} \sum_{i:\mathbf{x}^i \in
    \mathcal{S}_k} f^s(\mathbf{x}^i)
\end{equation}
%
Their method has significant computational advantages and allows the
recomputation of the accumulated effect with different bin-splitting
with near-zero additional computational cost. Moreover, by avoiding
the use of artificial samples at the bin limits DALE allows the use of
wider bins without out-of-distribution sampling. \todo{Maybe connect with our work}. In both cases, the
approximations partition the feature domain in \(K\) equally-sized
bins, without considering the underlying local effects.

@@

\begin{equation}
  \label{eq:ALE_var}
  \sigma^2(z) = \mathbb{E}_{X_c|X_s=z}\left [ \left (\dfdx (z, X_c) - \mu(z) \right )^2 \right ] 
\end{equation}
\noindent
The uncertainty emerges from (a) the feature correlations and (b) the
implicit feature interactions of the black-box function. We also
define the accumulated uncertainty at \(x_s\), as the accumulation of
the standard deviation of the local effects:

@@

Here, we activate the interaction term, i.e., \(a=1\), keeping the
weights equal \(a_1=a_2=1\) and \(\sigma_3^2=\frac{1}{4}\). In this
case, it is not straightforward to define the ground-truth effect for
features \(x_1, x_3\), because the interaction term provokes
heterogeneous instance-level effects, i.e., the instance-level effect
of \(x_1\) depend on the unknown value of \(x_3\) and vice-versa. We
observe that UALE's feature effects are quite intuitive. The average
effect of \(x_1\) is the same with the Example (a) with an added
uncertainty, reflecting the uncertainty about the instance-level
effects which is the standard deviation of \(x_3\), i.e.,
\(\sigma_3 = \frac{1}{2}\). The effect of \(x_3\) is only due to the
interaction term, therefore, the instance-level effects
\(\frac{\partial f}{\partial x_3} = x_1 \) follow
\(p(x_1) \sim \mathcal{U}(0,1)\) which has \(\mu_{x_1}=\frac{1}{2}\)
and \(\sigma_{x_1}=\frac{1}{4}\). This is reflected, in UALE's
estimations of Figure~\ref{fig:ex-synth-1-3}.

@@

\appendix

\section{List with Symbols}
\label{sec:list-with-symbols}

\section{Show that is unbiased estimator}
\label{sec:proof-1}

\section{Proof of Theorem~\ref{sec:theorem-1}}
\label{sec:proof-of-3-1}

\section{Proof of Corollary~\ref{sec:coroll-1}}
\label{sec:proof-of-coroll}

\section{Dynamic Programming}
\label{sec:dynamic-programming}

\todo{Review all the description}
For achieving a computationally-grounded solution we set a threshold
\(K_{max}\) on the maximum number of bins which also discretizes the
solution space. The width of the bin can take discrete values that are
multiple of the minimum step
\(u = \frac{x_{s, max} - x_{s, min}}{K_{max}}\). For defining the
solution, we use two indexes. The index
\(i \in \{0, \ldots, K_{max}\}\) denotes the point \((z_i)\) and the
index \(j \in \{0, \ldots, K_{max}\} \) denotes the position of the
\(j\)-th multiple of the minimum step, i.e., 
\(x_j = x_{s,min} + j \cdot u\). The recursive cost function
\(T(i,j)\) is the cost of setting \(z_i=x_j\):
\begin{equation}
  \label{eq:recursive_cost}
  \mathcal{T}(i,j) = \mathrm{min}_{l \in \{0, \ldots, K_{max}\}} \left [ \mathcal{T}(i-1, l) + \mathcal{B}(x_l, x_j) \right ]
\end{equation}
%
where \(\mathcal{T}(0,j)\) equals zero if \(j=0\) and \(\infty\) in
any other case. \(\mathcal{B}(x_l, x_j)\) denotes the cost of creating a bin
with limits \([x_l, x_j)]\):

\begin{itemize}
\item Discuss more aspects (e.g. Computational complexity)
\end{itemize}

>>>>

\begin{abstract}
  Accumulated Local Effects (ALE) is a popular explainable AI method that quantifies how a feature influences the decisions of a model, handling well feature correlations. In case of complex interactions between features, instance-level feature effects may deviate from the ALE curve. It is crucial to quantify this deviation, namely, the uncertainty of the global effect. In this work, we define Uncertainty-aware ALE (UALE) to quantify and visualize, on a single plot, both the average effect and its uncertainty. We show that UALE quantifies uncertainty effectively, even in case of correlated features. We also note that as in ALE, UALE's approximation requires partitioning the feature domain into non-overlapping intervals (bin-splitting). The average effect and the uncertainty are computed from the instances that lie in each bin. We formally prove that to achieve an unbiased approximation of the uncertainty in each bin, bin-splitting must follow specific constraints. Based on this, we propose a method to determine the optimal intervals, balancing the estimation bias and variance. We demonstrate, through synthetic and real datasets, (a) the advantages of modeling the uncertainty with UALE compared to alternative methods and (b) the effectiveness of UALE's appropriate bin splitting for accurately approximating of the average effect and its uncertainty.
\end{abstract}

@@

Recently, Machine Learning (ML) has been widely adopted in mission critical domains, such as healthcare and finance. In such high-stakes areas, it is important not only to provide accurate predictions but also meaningful explanations. For this reason, there is an increased interest in Explainable AI (XAI). XAI literature distinguishes between local and global methods~\citep{Molnar2020interpretable}. Local methods provide instance-level explanations, i.e., explain the prediction for a specific instance, whereas global methods summarize the entire model behavior, aggregating the instance-level explanations into a single interpretable outcome, usually a number or a plot.

A popular class of global XAI are feature effect (FE) methods~\citep{Gromping2020MAEP} that quantify the average (across all instances) effect of a single feature on the output. There are three widely-used FE methods: \emph{Partial Dependence Plots} (PDP)~\citep{friedman2001greedy}, \emph{Marginal Plots} (MP)~\citep{apley2020visualizing} and \emph{Accumulated Local Effects} (ALE)~\citep{apley2020visualizing}. ALE is established as the state-of-the-art, since PDP and MP have been criticized~\citep{baniecki2021fooling, Gromping2020MAEP} of providing misleading explanations in case of correlated input features.

In case of complex interactions between features, the instance-level (local) feature effects may exhibit significant deviation, aka heterogeneity, from the aggregated (global) explanation, a phenomenon known as aggregation bias~\citep{mehrabi2021survey}. We call this deviation \emph{the uncertainty of the global effect}\footnote{In the paper, the \emph{uncertainty of the global effect} and the \emph{heterogeneity of instance-level effects} are used interchangeably and refer to the deviation of instance-level (local) effects from the averaged feature effect curve (global).}. Aggregation bias leads to ambiguities. For example, a feature with zero average effect may indicate (a) no effect on the output or (b) highly positive effect for some instances and highly negative for some others. As a result, there is a need for FE methods to quantify the deviation of instance-level explanations, in addition to the average effect. In the case of PDP, such deviation is visualized via the Individual Conditional Explanations (ICE)~\citep{goldstein2015peeking}. ICE plots, however, have the same limitations as PDP in case of correlated features. No method to quantify the deviation of instance-level effects has been proposed for ALE.

In this work, we propose UALE, a global feature-effect method that extends ALE for modeling the uncertainty of the feature effect. Our method handles well cases with correlated features.  As in ALE, we provide an interval-based formulation of UALE. This formulation partitions the feature domain into non-overlapping intervals (bin-splitting) and defines the average effect (bin-effect) and its uncertainty (bin-uncertainty). We use this formulation to provide an UALE approximation. As we formally prove, a fixed equi-width partitioning that does not consider the characteristics of the instance-level effects, which is the case in ALE approximation, may lead to an erroneous (biased) estimation of the uncertainty.  Therefore, we propose a variable-width partitioning that leads to an unbiased approximation. The contributions of this paper are:

\begin{itemize}
\item A global feature effect method (UALE) that quantifies both the average effect and its uncertainty, i.e.,~the heterogeneity of instance-level effects.
\item An unbiased approximation of the uncertainty through an appropriate variable-size bin partitioning of the feature domain.
\item The evaluation of UALE on both synthetic and real datasets.
\end{itemize}

@@

In the rest of the paper, we use following notation. Let \(\mathcal{X} \in \mathbb{R}^d\) be the \(d\)-dimensional feature space, \(\mathcal{Y} \in \mathbb{R}\) the target space and \(f(\cdot) : \mathcal{X} \rightarrow \mathcal{Y}\) the black-box function. We use index \(s \in \{1, \ldots, d\}\) for the feature of interest and \(c = \{1, \ldots, d\} - s\) for the set with all other indexes. For convenience, we denote the feature vector \(\xb = (x_1, \cdots , x_s, \cdots, x_D)\) with \((x_s, \xc)\) and the corresponding random variables \(X = (X_1, \cdots , X_s, \cdots, X_D)\) with \((X_s, X_c)\). The training set is \(\mathcal{D} = \{(\xb^i, y^i)\}_{i=1}^N\) sampled i.i.d. from the distribution \(\mathbb{P}_{X,Y}\). Finally, we use \(f^{\mathtt{<method>}}(x_s)\) for denoting the effect of the \(s\)-th, where \(\mathtt{<method>}\) indicates the particular method in use, e.g., ALE.

\subsection{Feature Effect Methods}
\label{sec:feat-effect-meth}

The three well-known feature effect methods are: \emph{Partial Dependence Plots} (PDP), \emph{Marginal Plots} (MP) and \emph{Accumulated Local Effects} (ALE).  PDP formulates the global FE as an expectation over the distribution of \(X_c\), i.e., \(f^{\mathtt{PDP}}(x_s) = \mathbb{E}_{X_c}[f(x_s,X_c)]\), whereas MP as an expectation over the distribution of \(X_c|X_s\), i.e., \(f^{\mathtt{MP}}(x_s) = \mathbb{E}_{X_c|x_s}[f(x_s, X_c)]\). Both methods suffer from misestimations when features are correlated. PDP integrates over unrealistic instances and MP computes aggregated effects, i.e., imputes the combined effect of sets of features to a single feature~\citep{apley2020visualizing}.

@@

ICE plots and similar methods (e.g., d-ICE plots~\citep{goldstein2015peeking}) provide a set of curves illustrated on top-of PDP. Each curve corresponds to one instance of the dataset, \(f^{\mathtt{ICE}}_i(x_s) = f(x_s, \xc^i)\). The user then visually observes if the curves are homogeneous, i.e., all instances have similar effect plots, and to what extent they deviate from the PDP. Some approaches~\citep{herbinger2022repid, britton2019vine, molnar2020model} automate the aforementioned visual exploration, by grouping ICE plots into clusters. Unfortunately, these methods are subject to the failure modes of PDPs in cases of correlated features.

@@

To the best of our knowledge no work exist so far that quantifies the heterogeneous effects (uncertainty) based on the formulation of ALE.

@@

ALE is estimated from the available dataset instances. \citep{apley2020visualizing} proposed to divide the domain of the \(s\)-th feature in \(K\) equal-size bins and estimate the bin-effects from the instances that lie in each bin after setting the \(s\)-th feature at the bin limits:

\begin{equation}
  \label{eq:ALE_accumulated_mean_est}
  \hat{f}^{\mathtt{ALE}}(x_s) = \sum_{k=1}^{k_x} \frac{1}{|\mathcal{S}_k|} \sum_{i:\mathbf{x}^i \in
    \mathcal{S}_k} \left [ f(z_{k}, \xc^i) - f(z_{k-1}, \xc^i)) \right ]
\end{equation}
%
where \(k_x\) the index of the bin such that \(z_{k_x-1} \leq x_s < z_{k_x} \) and \(\mathcal{S}_k\) is the set of the instances of the \(k\)-th bin, i.e.  \( \mathcal{S}_k = \{ \xb^i : z_{k-1} \leq x^i_s < z_{k} \} \). \citep{gkolemis22} proposed the Differential ALE (DALE) that computes the local effects on the training instances using auto-differentiation:

\begin{equation}  \label{eq:DALE_accumulated_mean_est}
  \hat{f}^{\mathtt{DALE}}(x_s) = \Delta x \sum_{k=1}^{k_x} \frac{1}{|\mathcal{S}_k|} \sum_{i:\mathbf{x}^i \in
    \mathcal{S}_k} f^s(\mathbf{x}^i)
\end{equation}
%
Their method has significant computational advantages and allows the recomputation of the accumulated effect with a modified bin-splitting with near-zero additional computational cost. Moreover, by avoiding the use of artificial samples at the bin limits DALE allows the use of wider bins without out-of-distribution sampling. In both cases, the approximations partition the feature domain in \(K\) equally-sized bins, without considering the underlying local effects.

@@

\begin{equation}
  \label{eq:ALE_var}
  \sigma^2(z) = \mathbb{E}_{X_c|X_s=z}\left [ \left (\dfdx (z, X_c) - \mu(z) \right )^2 \right ] 
\end{equation}

\noindent
The uncertainty emerges from (a) the feature correlations and (b) the implicit feature interactions of the black-box function. We also define the accumulated uncertainty at \(x_s\), as the accumulation of the standard deviation of the local effects:

@@

Here, we activate the interaction term, i.e., \(a=1\), keeping the weights equal \(a_1=a_2=1\) and \(\sigma_3^2=\frac{1}{4}\). In this case, it is not straightforward to define the ground-truth effect for features \(x_1, x_3\), because the interaction term provokes heterogeneous instance-level effects, i.e., the instance-level effect of \(x_1\) depend on the unknown value of \(x_3\) and vice-versa. We observe that UALE's feature effects are quite intuitive. The average effect of \(x_1\) is the same with the Example (a) with an added uncertainty, reflecting the uncertainty about the instance-level effects which is the standard deviation of \(x_3\), i.e., \(\sigma_3 = \frac{1}{2}\). The effect of \(x_3\) is only due to the interaction term, therefore, the instance-level effects, \(\frac{\partial f}{\partial x_3} = x_1 \), follow \(p(x_1) \sim \mathcal{U}(0,1)\) which has \(\mu_{x_1}=\frac{1}{2}\) and \(\sigma_{x_1}=\frac{1}{4}\). This is reflected, in UALE's estimations of Figure~\ref{fig:ex-synth-1-3}. We note that PDP-ICE provide (a) for \(x_1\) a near-zero average effect plot, which is not intuitive and (b) for \(x_3\) a plot that, roughly, matches with UALE.

@@

% \appendix

% \section{List with Symbols}
% \label{sec:list-with-symbols}

% \section{Show that is unbiased estimator}
% \label{sec:proof-1}

% \section{Proof of Theorem~\ref{sec:theorem-1}}
% \label{sec:proof-of-3-1}

% \section{Proof of Corollary~\ref{sec:coroll-1}}
% \label{sec:proof-of-coroll}

% \section{Dynamic Programming}
% \label{sec:dynamic-programming}

% \todo{Review all the description}
% For achieving a computationally-grounded solution we set a threshold
% \(K_{max}\) on the maximum number of bins which also discretizes the
% solution space. The width of the bin can take discrete values that are
% multiple of the minimum step
% \(u = \frac{x_{s, max} - x_{s, min}}{K_{max}}\). For defining the
% solution, we use two indexes. The index
% \(i \in \{0, \ldots, K_{max}\}\) denotes the point \((z_i)\) and the
% index \(j \in \{0, \ldots, K_{max}\} \) denotes the position of the
% \(j\)-th multiple of the minimum step, i.e., 
% \(x_j = x_{s,min} + j \cdot u\). The recursive cost function
% \(T(i,j)\) is the cost of setting \(z_i=x_j\):
% \begin{equation}
%   \label{eq:recursive_cost}
%   \mathcal{T}(i,j) = \mathrm{min}_{l \in \{0, \ldots, K_{max}\}} \left [ \mathcal{T}(i-1, l) + \mathcal{B}(x_l, x_j) \right ]
% \end{equation}
% %
% where \(\mathcal{T}(0,j)\) equals zero if \(j=0\) and \(\infty\) in
% any other case. \(\mathcal{B}(x_l, x_j)\) denotes the cost of creating a bin
% with limits \([x_l, x_j)]\):

% \begin{equation}
%   \label{eq:cost_step}
%   \mathcal{B}(x_l, x_j) = \begin{cases}
%                             \infty, & \text{if $x_j > x_l$ or \(|\mathcal{S}_{(x_j, x_l)}| < N\)}\\
%                             0, & \text{if $x_j = x_l$}\\
%                             \hat{\sigma}^2(x_j, x_l), &\text{if $x_j \leq x_l$}
%   \end{cases}
% \end{equation}

% The optimal solution is given by solving
% \(\mathcal{L} = \mathcal{T}(K_{max}, K_{max})\) and keeping track of the sequence of
% steps.

% \noindent

% \begin{itemize}
% \item Discuss more aspects (e.g. Computational complexity)
% \end{itemize}
